# tbl_hierarchical()

## Adverse Event Reporting (and friends)

Use `tbl_hierarchical()` and `tbl_hierarchical_count()` for reporting of AEs, Con Meds, and more.

```{r}
#| label: create-ae-tbl
tbl_ae <- adae |>
  tbl_hierarchical(
    by = "ARM2",
    variables = c("AESOC", "AEDECOD"),
    id = "USUBJID",
    denominator = adsl
  )
```

```{r}
#| echo: false
#| label: print-ae-tbl
tbl_ae
```

## Add an overall column {auto-animate="true"}

```{r}
#| label: 'ae-add-overall'
#| output-location: "column"
#| code-line-numbers: "2"
tbl_ae |>
  add_overall(last = TRUE)
```

-   `add_overall()`: adds an all-treatment-arms column, `last = TRUE` places it on the right

## Sort by frequency {auto-animate="true"}

```{r}
#| label: 'ae-sort'
#| output-location: "column"
#| code-line-numbers: "2"
tbl_ae |>
  sort_hierarchical()
```

-   `sort_hierarchical()`: orders rows by descending event frequency (default)

-   Use `sort = everything() ~ "alphanumeric"` to sort alphabetically instead

## Filter to common events {auto-animate="true"}

```{r}
#| label: 'ae-filter'
#| output-location: "column"
#| code-line-numbers: "2,3,4"
tbl_ae |>
  sort_hierarchical() |>
  filter_hierarchical(sum(n) >= 5)
```

-   `filter_hierarchical()`: keeps AEs meeting an occurrence threshold

-   The filter is an expression on the underlying counts, e.g. `sum(n) >= 5`, `n_overall > 20`, or `p_overall > 0.05`

## Adverse event differences

```{r}
#| label: 'ae-add-difference'
#| output-location: "column"
#| code-line-numbers: "2"
tbl_ae |>
  add_difference()
```

-   `add_difference()`: risk differences between arms, with confidence intervals (gtsummary 2.6.0)
