# tbl_hierarchical()

## Adverse Event Reporting (and friends)

Use `tbl_hierarchical()` and `tbl_hierarchical_count()` for reporting of AEs, Con Meds, and more.

```{r}
#| label: create-ae-tbl
#| output-location: "column"
tbl_ae <- adae |>
  tbl_hierarchical(
    by = "ARM2",
    variables = c("AESOC", "AEDECOD"),
    id = "USUBJID",
    denominator = adsl
  )
tbl_ae
```

::: {.small}
The same `add_*()` and `modify_*()` verbs work here too, e.g. `add_overall(last = TRUE)` and `add_difference()` for risk differences between arms.
:::

## Sort and filter the hierarchy

```{r}
#| label: 'ae-sort-filter'
#| output-location: "column"
tbl_ae |>
  sort_hierarchical() |>
  filter_hierarchical(sum(n) >= 5)
```

::: {.small}
-   `sort_hierarchical()`: orders rows by descending event frequency (default). Use `sort = everything() ~ "alphanumeric"` to sort alphabetically instead

-   `filter_hierarchical()`: keeps AEs meeting an occurrence threshold. The filter is an expression on the underlying counts, e.g. `sum(n) >= 5`, `n_overall > 20`, or `p_overall > 0.05`
:::
